---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ceiglobal

<!-- badges: start -->
[![](https://img.shields.io/badge/lifecycle-Experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#Experimental)
![](https://img.shields.io/badge/Most%20used%20package-in%20CEI-green.svg)
<!-- badges: end -->

The goal of ceiglobal is to provide an easy to use extension to `ggplot2` to allow users to easily create beautiful figures consistent with CEI's style guide.

## Installation

This is a 'private' package that you can only install if you are a member of the ceiglobal organisation on github. To obtain access you will need: a) a github account, b) access to CEI's organisation on github, c) a personal access token (PAT) to prevent unauthorised access and d) a couple of lines of code to install. The steps for each are outlined below.

### Get a github account

This is nice and easy. Go to [github.com](www.github.com) and sign up for a free account and pick a username. Your username can be anything, it doesn't have to be work-related.

### Get access to CEI's organisation on github

Send Dave your github username and he'll add you manually.

### Get a personal access token so you can download the package

This is a little tricker, but we'll walk you through it.

The personal access token prevents any unauthorised access to our repositories on github. 

1. Go [here](https://github.com/settings/tokens)
2. Select "generate access token"
3. Add a note in the box to remind yourself what this is for, something like "theme_ceiglobal". 
4. Select the checkbox called "repo", scroll to the bottom and "generate token"
5. You will be taken to a new page with your PAT create a copy of it
6. You need to store this PAT in your R profile, do this in RStudio by running the code `usethis::edit_r_profile()`
7. This will open up a new tab called `.RProfile*`. You'll need to run another bit of code `Sys.setenv(GITHUB_PAT = "this is where you paste you PAT")` then save code and close it.
8. All done, RStudio now has a record of your PAT!

### Final installation

You can on install this package by running this code below. Note: you will need the install and load the package `devtools` first. To install run `install.package("devtools")`, to load run`library("devtools")`. 

Install `ceiglobal` by running:

``` r
devtools::install_github("ceiglobal/ceiglobal")
```

## Example

This is a very basic example which shows you how to the package takes a standard `ggplot2` object and applies CEI's style guide.

```{r example, echo=TRUE, message=FALSE, warning=FALSE}
## LOAD PACKAGES

library(ggplot2)
library(ceiglobal)

## This what a plot looks like using standard ggplot2 output

diamonds %>%
  ggplot() +
  aes(x = carat, y = price, colour = color) +
  geom_point() +
  facet_wrap(~cut, ncol = 1)

## This is what happens when you sprinkle a little bit of cei magic on it

diamonds %>%
  ggplot() +
  aes(x = carat, y = price, colour = color) +
  geom_point() +
  facet_wrap(~cut, ncol = 1) +
  theme_ceiglobal()
```
