---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ceiglobal

<!-- badges: start -->
use_lifecycle_badge("Experimental")
<!-- badges: end -->

The goal of ceiglobal is to provide an easy to use extension to `ggplot2` to allow users to easily create beautiful figures consistent with CEI's style guide.

## Installation

This is a 'private' package that you can only install if you are a member of the ceiglobal organisation on github. To gain access you will need a github account and for the administrator to add you. 

You can on install this package by running this code below. Note: you will need the install and load the package `devtools` first. To install run `install.package("devtools")`, to load run`library("devtools")`. 

Install `ceiglobal` by running:

``` r
devtools::install_github("ceiglobal/ceiglobal")
```

## Example

This is a very basic example which shows you how to the package takes a standard `ggplot2` object and applies CEI's style guide.

```{r example}
## LOAD PACKAGES

library(ggplot2)
library(ceiglobal)

## This what a plot looks like using standard ggplot2 output

diamonds %>%
  ggplot() +
  aes(x = carat, y = price, colour = color) +
  geom_point() +
  facet_wrap(~cut, ncol = 1)

## This is what happens when you sprinkle a little bit of cei magic on it

diamonds %>%
  ggplot() +
  aes(x = carat, y = price, colour = color) +
  geom_point() +
  facet_wrap(~cut, ncol = 1) +
  theme_ceiglobal()
```
